### 2025-02-19 tfp2025 3/src/sections/4-discussion.tex
work

\jr{TODO: μ-regular expressions have been studied before, cite}
\paragraph{Expressiveness} We conjecture that our grammars which include variables and fixed points can describe any context-free language. We have shown the example of balanced the bracket language which is known to be context-free. Furthermore, Grenrus shows that any context-free grammar can be converted to his grammars \cite{fix-ing-regular-expressions}, which are similar to our grammars. The main problem is showing that mutually recursive nonterminals can be expressed using our simple fixed points, which requires Beki\'c's bisection lemma~\cite{Bekic1984}. Formalizing this in our framework is future work.

@@

\paragraph{Simplicity}
One of the main contributions of Elliott's type theoretic formalization of languages~\cite{conal-languages} is its simplicity of implementation and proof. To be able to extend his approach to context-free languages we have had to introduce some complications.
\jr{TODO: finish this paragraph}
% Most notably, we use fuel to define the semantics of our grammars. We have explored other approaches such as using guarded type theory, but we did not manage to significantly simplify our formalization. Furtheremore, we expect that many proofs remain simple despite our fuel-based approach.
\medbreak

In conclusion, we have formalized (acyclic) context-free grammars using a type theoretic approach to provide fertile ground for further formalizations of disambiguation strategies and parsers that are both correct and performant.

>>>>

\jr{TODO: μ-regular expressions have been studied before, cite}
\paragraph{Expressiveness} We conjecture that our grammars which include variables and fixed points can describe any context-free language.
\jr{mention that we only support context-free languages without mutual recursion and how we use a subset of μ-regular languages}.
% We have shown the example of balanced the bracket language which is known to be context-free. Furthermore, Grenrus shows that any context-free grammar can be converted to his grammars \cite{fix-ing-regular-expressions}, which are similar to our grammars. The main problem is showing that mutually recursive nonterminals can be expressed using our simple fixed points, which requires Beki\'c's bisection lemma~\cite{Bekic1984}. Formalizing this in our framework is future work.

@@

\paragraph{Simplicity}
One of the main contributions of Elliott's type theoretic formalization of languages~\cite{conal-languages} is its simplicity of implementation and proof. To be able to extend his approach to context-free languages we have had to introduce some complications.
\jr{TODO: finish this paragraph}
% Most notably, we use fuel to define the semantics of our grammars. We have explored other approaches such as using guarded type theory, but we did not manage to significantly simplify our formalization. Furtheremore, we expect that many proofs remain simple despite our fuel-based approach.
